---
title: "Structural brain correlates of the externalizing spectrum in young adults"
output: html_document
---

# Libraries and setup

```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
library(readr)
library(brms)
library(tidyverse)
library(tidybayes)
library(psych)
library(GPArotation)
library(gt)
library(kableExtra)
library(flextable)
library(officer)
library(ggseg)
library(patchwork)

overwrite <- FALSE
overwrite_brms <- FALSE
overwrite_latex_table <- FALSE

seed <- 2020
cores <- 8
chains <- 8
iter <- 4000
warmup <- 2000
refresh <- 0
```

# Specify brms models

```{r message=FALSE, warning=FALSE, include=FALSE}

# correlation
if (!file.exists(here("analysis/scripts/brms/brms_robust_correlation.rds")) || overwrite_brms == TRUE) {
  set.seed(seed)
  
  temp_data <- 
    data.frame(x = rnorm(50),
               y = rnorm(50))
  
  brms_robust_correlation <- 
    brm(mvbind(x, y) ~ 0,
        data = temp_data,
        family = student,
        prior = c(prior(gamma(2, 0.1), class = nu),
                  prior(normal(0, 10), class = sigma, resp = x),
                  prior(normal(0, 10), class = sigma, resp = y),
                  prior(lkj(2), class = rescor)),
        iter = iter,
        cores = cores,
        chains = chains,
        warmup = warmup,
        seed = seed,
        refresh = refresh)

  saveRDS(brms_robust_correlation, here("analysis/scripts/brms/brms_robust_correlation.rds"))
}

# linear regression

if (!file.exists(here("analysis/scripts/brms/brms_robust_linear_regression.rds")) || overwrite_brms == TRUE) {
  set.seed(seed)
  
  temp_data <- 
    data.frame(y = rnorm(50),
               x1 = rnorm(50),
               x2 = rnorm(50),
               x3 = rnorm(50))
  
  brms_robust_linear_regression <-
    brm(y ~ 0 + x1 + x2 + x3,
        data = temp_data,
        family = student,
        prior = c(prior(normal(0, 10), class = b),
                  prior(gamma(2, 0.1), class = nu),
                  prior(cauchy(0, 1),  class = sigma)),
        iter = iter,
        cores = cores,
        chains = chains,
        warmup = warmup,
        seed = seed,
        refresh = refresh)
  
  saveRDS(brms_robust_linear_regression, here("analysis/scripts/brms/brms_robust_linear_regression.rds"))
}
```

# Read data

```{r message=FALSE, warning=FALSE, include=FALSE}
source(here("analysis/scripts/r/01_helper_functions.R"))
source(here("analysis/scripts/r/02_esi_data_transform.R"))
source(here("analysis/scripts/r/03_read_and_process_data.R"))
```

# Reliability analysis

```{r echo=FALSE, message=FALSE, warning=FALSE}
source(here("analysis/scripts/r/04_reliability_analysis.R"))
readRDS(here("analysis/data/reliability_data.rds")) %>%
  gt()
```

# Descriptives

## Gender distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(gender) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

## Age

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  na.omit() %>%
  select(age) %>%
  describe() %>%
  select(mean, sd, median, min, max) %>%
  mutate_if(is.numeric, round, 2) %>%
  gt()
```

## Years of education total

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  na.omit() %>%
  select(years_of_education_total) %>%
  describe() %>%
  select(mean, sd, median, min, max) %>%
  mutate_if(is.numeric, round, 2) %>%
  gt()
```

## Any previous or current psychiatric disorders

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(psychiatric_disorders) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

## Which previous or current psychiatric disorders

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(psychiatric_disorders_2) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

## Any previous or current neurological disorders

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(neurological_disorders) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

## Any current medication

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(current_medication) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

## Which current medication

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
data %>%
  group_by(current_medication_2) %>%
  na.omit() %>%
  summarise(n = n()) %>%
  mutate(perc = round(n / sum(n) * 100, 1)) %>%
  gt()
```

# Table 1

```{r echo=FALSE, message=FALSE, warning=FALSE}
data <- readRDS(here("analysis/data/data.rds"))
table_1 <- 
  data %>%
  na.omit() %>%
  # rename
  mutate("ESI-BF_DIS" = general_disinhibition,
         "ESI-BF_AGG" = callous_aggression,
         "ESI-BF_SUB" = substance_abuse,
         "NoGo accuracy" = nogo_accuracy,
         "Left caudal ACC" = lcaudalanteriorcingulate,
         "Right caudal ACC" = rcaudalanteriorcingulate,
         "Left rostral ACC" = lrostralanteriorcingulate,
         "Right rostral ACC" = rrostralanteriorcingulate,
         "Left lateral OFC" = llateralorbitofrontal,
         "Right lateral OFC" = rlateralorbitofrontal,
         "Left medial OFC" = lmedialorbitofrontal,
         "Right medial OFC" = rmedialorbitofrontal,
         "Left DLPFC" = lrostralmiddlefrontal,
         "Right DLPFC" = rrostralmiddlefrontal) %>%
  # order
  select("ESI-BF_DIS",
         "ESI-BF_AGG",
         "ESI-BF_SUB",
         # go/nogo
         "NoGo accuracy",
         # left hemisphere
         "Left caudal ACC",
         "Left rostral ACC",
         "Left lateral OFC",
         "Left medial OFC",
         "Left DLPFC",
         # right hemisphere
         "Right caudal ACC",
         "Right rostral ACC",
         "Right lateral OFC",
         "Right medial OFC",
         "Right DLPFC") %>%
  describe() %>%
  add_rownames(., var = "rowname") %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(mean_sd = paste0(mean, " ± ", sd),
         range = paste0(min, " - ", max)) %>%
  select(rowname, mean_sd, range) %>%
  kable("latex",
        booktabs = TRUE,
        col.names = c("Variable",
                      "Mean ± SD",
                      "Range"),
        align = c('l','c','c'))

if (!file.exists(here("manuscript/tables/table_1.tex")) || overwrite_latex_table == TRUE) {
  write(table_1, file = here("manuscript/tables/table_1.tex"))
}
```

# Correlations

```{r message=FALSE, warning=FALSE, include=FALSE}
source(here("analysis/scripts/r/05_robust_correlations.R"))
correlation_results %>% 
  mutate_if(is.numeric, round, 2) %>%
  gt()
```

# Linear regressions

```{r message=FALSE, warning=FALSE, include=FALSE}
source(here("analysis/scripts/r/06_robust_linear_regression.R"))
```

## Table 2

```{r message=FALSE, warning=FALSE, include=FALSE}
source(here("analysis/scripts/r/07_regression_table.R"))

table_2 <-
  kable(tmp,
        "latex",
        booktabs = TRUE,
        align = c('l','c','c','c','c','c','c', 'c')) %>%
  kable_styling() %>% 
  add_header_above(c(" " = 1, "ESI-BF_DIS" = 2, "ESI-BF_AGG" = 2, "ESI-BF_SUB" = 2, "NoGo accuracy" = 2)) %>%
  pack_rows("Left", 1, 5) %>%
  pack_rows("Right", 6, 10)
```

# Figures

```{r message=FALSE, warning=FALSE, include=FALSE}
source(here("analysis/scripts/r/08_figures.R"))
```

# Session info

```{r echo=FALSE, message=FALSE, warning=FALSE}
devtools::session_info()
```












